\documentclass{createspace}

% https://tex.stackexchange.com/questions/69901/how-to-typeset-greek-letters
\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}

\usepackage{xcolor}
\usepackage{tcolorbox}
\newtcolorbox{etymology_box}{colback=blue!5!white, colframe=blue!75!black,fonttitle=\bfseries,title=Etymologia}

\usepackage{lscape} % https://www.tablesgenerator.com/
\usepackage{makecell}

\usepackage{siunitx}
\usepackage[version=4]{mhchem}

\newcommand{\important}[1]{{\color{blue!70!white}\textbf{#1}}}

\usepackage{etoolbox} % https://tex.stackexchange.com/questions/492461/showidx-gives-undefined-control-sequence-error
% forced by -output-directory option in makefile
% see https://tex.stackexchange.com/a/564296
\makeatletter
\patchcmd\imki@putindex
  {\imki@exec{\imki@program \imki@options #1.idx}}
  {\imki@exec{cd ../../build/textbook;\imki@program\imki@options#1.idx}}
  {\message{Patch succeeded in imki@putindex}}
  {\errmessage{Patch failed in imki@putindex}}
\makeatother

\makeindex[title=Skorowidz]
\makeindex[name=persons,title=Indeks osób]

\author{Aallotar Järvinen}
\title{Chemiczne notatki}

\begin{document}
\input{00_intro/head_1}
\input{00_intro/head_2}
\input{00_intro/head_3}
\input{00_intro/head_4}
\input{00_intro/head_5}
\tableofcontents

\chapter{Budowa atomu i cząsteczki. Układ okresowy pierwiastków}
% Jones, Atkins: 1, 7, 9
\input{01_atoms/01_history}
\input{01_atoms/02_quantum}

\chapter{Wiązania chemiczne}
% Jones, Atkins: 8

\chapter{Gazy}
% Jones, Atkins: 5
\input{03_gases/01_intro}

\chapter{Ciecze i ciała stałe}
% Jones, Atkins: 10
\input{04_solids_liquids/01_intro}

\chapter{Związki nieorganiczne}
% Jones, Atkins: 15
\input{05_inorganic/01_oxide}
\input{05_inorganic/02_acid}
\input{05_inorganic/03_hydroxide}
\input{05_inorganic/04_salt}

\chapter{Stechiometria}
\input{06_stoichiometry/01_intro}
% Jones, Atkins: 2, 4

\chapter{Reakcje chemiczne}
% Jones, Atkins: 3
\input{07_reactions/01_intro}
\input{07_reactions/02_precipitation}
\input{07_reactions/03_acid_base}
\input{07_reactions/04_redox}
Sekcja \ref{section_chemical_reactions_intro} na podstawie \cite[s. 91-97]{jones_atkins}.
Sekcja \ref{section_chemical_reactions_redox} na podstawie \cite[s. 118-126]{jones_atkins}.

\chapter{Roztwory}
% Jones, Atkins: 12
\input{08_solutions/01_solutions}
\input{08_solutions/02_separation}
\input{08_solutions/03_sol}
\input{08_solutions/04_solubility}
\input{08_solutions/osmoza}
(Osmoza: na podstawie \cite[s. 584-586]{jones_atkins}).
\input{08_solutions/99_dict}

\chapter{Kinetyka chemiczna}
% Jones, Atkins: 13
\input{09_kinetics/01_intro}

\chapter{Równowaga chemiczna}
\input{10_equilibrium/01_intro}
% Jones, Atkins: 14, 16, 17?

\chapter{Termochemia}
\input{11_thermochemistry/01_intro}
% Jones, Atkins: 6

\chapter{Elektrochemia}
\input{12_electrochemistry/01_intro}
% Jones, Atkins: 18

\chapter{Reakcje w wodnych roztworach elektrolitów}

\chapter{Charakterystyka pierwiastków chemicznych}
% Jones, Atkins: 19, 20, 21
\input{14_blocks/01_1-2-13-14}

\input{14_blocks/02_15-16-17-18}

\input{14_blocks/03_d}

\chapter{Chemia jądrowa}
% Jones, Atkins: 22
\input{15_nuclear/01_intro}

\chapter{Chemia organiczna}
% Jones, Atkins: 11

\raggedright
\bibliographystyle{alpha}
\bibliography{chemistry_notes}

\indexprologue{\small Tekst prologu I.}
\printindex

\indexprologue{\small Tekst prologu II.}
\printindex[persons]

\end{document}

To be done:
\textbf{strona 14}: tlenki?

\textbf{strona 15}: stechio

\textbf{strona 17}: redoks, antyutleniacze

\textbf{Strona 18}: ogniwo galwaniczne

\textbf{strona 19}: korozja, zabezpieczanie przed nią, elektroliza

\textbf{strona 20}: stopy (alloys), termit, stal (CORTEN)

\textbf{Strona 24}: równowaga chemiczna, symbol dwóch strazałek

\textbf{Strona 26}
Bezpieczeństwo
NFPA 704: standard wprowadzony w Stanach Zjednoczonych przez Narodowy Związek Ochrony Przeciwpożarowej (ang. National Fire Protection Association). Definiuje on diament ognia czyli charakterystyczny postawiony na wierzchołku kwadrat podzielony na cztery mniejsze kwadraty, używany przez służby ratunkowe do łatwej i szybkiej identyfikacji substancji, związanego z nią ryzyka, środków gaśniczych stosowanych do gaszenia pożaru, oraz innych zagrożeń i możliwości w czasie działań ratowniczych. 
Flammability (red)
0   Materials that will not burn under typical fire conditions (e.g. carbon tetrachloride), including intrinsically noncombustible materials such as concrete, stone, and sand. Materials that will not burn in air when exposed to a temperature of 820 °C (1,500 °F) for a period of 5 minutes.
1   Materials that require considerable preheating, under all ambient temperature conditions, before ignition and combustion can occur (e.g. mineral oil, ammonia). Includes some finely divided suspended solids that do not require heating before ignition can occur. Flash point at or above 93.3 °C (200 °F).
2   Must be moderately heated or exposed to relatively high ambient temperature before ignition can occur (e.g. diesel fuel, paper, sulfur and multiple finely divided suspended solids that do not require heating before ignition can occur). Flash point between 37.8 and 93.3 °C (100 and 200 °F).
3   Liquids and solids (including finely divided suspended solids) that can be ignited under almost all ambient temperature conditions (e.g. gasoline, acetone). Liquids having a flash point below 22.8 °C (73 °F) and having a boiling point at or above 37.8 °C (100 °F) or having a flash point between 22.8 and 37.8 °C (73 and 100 °F).
4   Will rapidly or completely vaporize at normal atmospheric pressure and temperature, or is readily dispersed in air and will burn readily (e.g. acetylene, propane, hydrogen gas, diborane). Includes pyrophoric substances. Flash point below room temperature at 22.8 °C (73 °F). 
Health (blue)
0   Poses no health hazard, no precautions necessary and would offer no hazard beyond that of ordinary combustible materials (e.g. wood, paper)
1   Exposure would cause irritation with only minor residual injury (e.g. acetone, sodium bromate, potassium chloride)
2   Intense or continued but not chronic exposure could cause temporary incapacitation or possible residual injury (e.g. diethyl ether, ammonium phosphate, carbon dioxide, iodine, chloroform, DEET).
3   Short exposure could cause serious temporary or moderate residual injury (e.g. liquid hydrogen, sulfuric acid, calcium hypochlorite, carbon monoxide, hexafluorosilicic acid, zinc chloride)
4   Very short exposure could cause death or major residual injury (e.g. hydrogen cyanide, phosgene, diborane, methyl isocyanate, hydrofluoric acid) 
Instability–reactivity (yellow)
0   Normally stable, even under fire exposure conditions, and is not reactive with water (e.g. helium, N2)
1   Normally stable, but can become unstable at elevated temperatures and pressures (e.g. propene)
2   Undergoes violent chemical change at elevated temperatures and pressures, reacts violently with water, or may form explosive mixtures with water (e.g. white phosphorus, potassium, sodium)
3   Capable of detonation or explosive decomposition but requires a strong initiating source, must be heated under confinement before initiation, reacts explosively with water, or will detonate if severely shocked (e.g. ammonium nitrate, caesium, diborane, hydrogen peroxide)
4   Readily capable of detonation or explosive decomposition at normal temperatures and pressures (e.g. nitroglycerin, chlorine dioxide, nitrogen triiodide, manganese heptoxide, TNT) 
Special notice (white)
The white "special notice" area can contain several symbols. The following symbols are defined by the NFPA 704 standard.
OX  Oxidizer, allows chemicals to burn without an air supply (e.g. potassium perchlorate, ammonium nitrate, hydrogen peroxide).
W   Reacts with water in an unusual or dangerous manner (e.g. caesium, sodium, diborane, sulfuric acid).
SA  Simple asphyxiant gas (specifically helium, nitrogen, neon, argon, krypton, xenon). The SA symbol shall also be used for liquefied carbon dioxide vapor withdrawal systems and where large quantities of dry ice are used in confined areas.[2]
Non-standard symbols (white)
These hazard codes are not part of the NFPA 704 standard, but are occasionally used in an unofficial manner. The use of non-standard codes may be permitted, required or disallowed by the authority having jurisdiction (e.g. fire department).
COR   Corrosive; strong acid or base (e.g. sulfuric acid, potassium hydroxide)
ACID  Acid or alkaline, to be more specific
ALK
BIO   Biological hazard (e.g. flu virus, rabies virus)
Biohazard symbol.svg
POI   Poisonous (e.g. strychnine, alpha-amanitin)
RA  Radioactive (e.g. plutonium, cobalt-60, carbon-14)
RAD
Radiation warning symbol2.svg
CRY   Cryogenic (e.g. liquid nitrogen) 

\textbf{Strona 29}: kataliza, katalizatory mechanizm, historia, ważne reakcje z nimi; enzymhy

\textbf{strona 32}: termodynamika

\textbf{Strona 33}: chemia analityczna - historia, czystosci :/ miks

\textbf{Strona 34}: miareczkowanie (titration)

\textbf{Strona 35}: kolory jonów

\textbf{Strona 37}: tlenki

\textbf{Strona 38}: hydroxides

\textbf{Strona 39}: kwasy -> tlen? tlenki?

\textbf{Strona 40}: sól, minerały, zwitterion

\textbf{Strona 41}: Teoria kwasów i zasad, Lavoisier 1776, Liebig 1838, Arrhenius, Ostwald, Bronsted-Lourwy, Lewis, Lux-Flood, Usanovich, HSAB (hard soft acid base) + borderline cases

\textbf{Strona 42}: skala pH, "the standard e.m.f."

\textbf{Strona 44}: Octane number

\textbf{Strona 45}: kinetyka chemiczna, Waage, Guldberg, reaction rate constant, reaction rate, mechanizm?, energia aktywacji, stała równowagi termodynamicznej, równanie vant Hoffa

\textbf{Strona 49}: teoria vsepr

\textbf{Strona 51}: moment dipolowy, 1 debye ... amphiphiles, soaps, detergents

\textbf{Strona 52}: Termochemia, Lavoisier/Laplace law, Hess law, calorimeter bomb


\textbf{Strona 55}: przemysł chemiczny w polsce

\textbf{Strona 56}: Antiknock agents, tetraetyllead

\textbf{Strona 57}: Strącanie, Redox?, Acid-base: neutralisation, double displacement

\textbf{Strona 59}: Sprzęt laboratoryjny (strona 59). a burette, a graduated cylinder, a volumetric flask, a pipette, a condenser, a desiccator, a distillation flask, a reaction flask, a reagent flask, a Buchner/suction flask, an Erlenmeyer flask, a beaker, a Denvar flask, a watch glass, a Petri dish, a stir rod, a Bunsen burner, a test tube.

\textbf{Strona 63}: Eksperymenty

\textbf{Strona 64}: A buffer solution, Magic numbers, Roztwarzanie, Solvation, Siddociation

\textbf{Strona 65}
% Farmakognozja (gr. φάρμακον (pharmakon) – lek i γνῶσις (gnosis) – wiedza) – dział farmacji, nauka o substancjach pochodzenia naturalnego, które są wykorzystywane jako leki[1].
In biology, poisons are substances that can cause death, injury or harm to organs, tissues, cells, and DNA usually by chemical reactions or other activity on the molecular scale, when an organism is exposed to a sufficient quantity.[1][2]
A toxin is a harmful substance produced within living cells or organisms;[1][2] synthetic toxicants created by artificial processes are thus excluded. The term was first used by organic chemist Ludwig Brieger (1849–1919),[3] derived from the word toxic.[4]
Venom is a type of poison, especially one secreted by an animal.[1] It is delivered in a bite, sting, or similar action. Venom has evolved in terrestrial and marine environments and in a wide variety of animals: both predators and prey, and both vertebrates and invertebrates.
Pesticides are substances that are meant to control pests.[1] The term pesticide includes all of the following: herbicide, insecticides (which may include insect growth regulators, termiticides, etc.) nematicide, molluscicide, piscicide, avicide, rodenticide, bactericide, insect repellent, animal repellent, antimicrobial, fungicide,[2] and lampricide.[3] The most common of these are herbicides which account for approximately 80\% of all pesticide use.[4] Most pesticides are intended to serve as plant protection products (also known as crop protection products), which in general, protect plants from weeds, fungi, or insects. As an example, the fungus Alternaria solani is used to combat the aquatic weed Salvinia.

\textbf{Strona 66}: Strychnina, cyjanek potasu

\textbf{Strona 67}: Historia chemii, Albertus Magnus, Paracelsus, Robert Boyle

\textbf{Strona 69}: mefedron XD

\textbf{Strona 71}: Radioaktywność: alpha decay,  geiger-nuttall law, gamov had solved 1928... beta decay, K-capture

\textbf{Strona 72}: The alnthanide contraction, S. Canmizzaro prepared chyanomamide by the action of ..., In Alessandria he discovered that for example benzaldehyde decomposes % https://www.chemeurope.com/en/encyclopedia/Stanislao_Cannizzaro.html ?

\textbf{Strona 73}: Kleje, Adhesive, also known as glue, cement, ... or paste is any nonmetallic, Non-reactive: drung ,pressure-sensitice adhesives, contact adhesives, hot-melt 

\textbf{Strona 74}: Reactive: anaerobic, multi-part, Polyurethane resin+one of ..., PMFS, one part, Thread-locking fluid (threadlocker)

\textbf{Strona 75}: Wymiary atomu (van der Waalsa, jonowy, kowalencyjny, metaliczny, Bohra)

\textbf{Strona 76}: Rydberg formula, Lyman, Balmer, ... series

\textbf{strona 77}: Fajans rules, ionic/covalent, displaced vby Paulings approach, States of matter, Band theory

\textbf{strona 78}: Band (forbidden) gaps. Fermi level. p-n junction, insulator?

\textbf{strona 79}: SURFACTANT, LITHIUM SOAPS, MINERAL OIL, VEGETABLE OILS, LACQUER, VARNISH, PAINT

\textbf{strona 80}: Pigments are granular solids incorporated ... ROZPUSZCZALNIK/ROZCIENCZALNIK, Nitro solvent